Andres Karjus

### 2019-02-20 index.Rmd
links

@@

- I have been developing materials on data visualization using R; these have been used during 2017-2019 in a number of different workshops for humanities and social science audiences, collectively under the name of _aRt of the Figure_ (all the materials and code available [here](https://andreskarjus.github.io/artofthefigure/)).
- One outlet for these has been through the PPLS Writing Centre - the dates and booking information are available [here](http://writingcentre.ppls.ed.ac.uk/workshops/). During the semester it's a 1-hour workshop, extended to 2 hours for the extracurricular summer edition.
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page -> Book an appointment -> look for my name in the list of tutors in the 'Select staff' dropdown menu.
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).

@@

- The aRt of the Figure, interactive plots edition at the CLE PhD retreat 2019
- The aRt of the Figure workshop as a full day session at the [Scottish Graduate School of Social Science Summer School 2018](http://www.socsciscotland.ac.uk/skills_and_training/summer_school).
- I was working with the PPLS Writing Centre in the summer of 2018 to provide a drop-in quantitative research help service for PPLS MSc students working on their theses.
- aRt of the Figure as an afternoon workshop for the annual Edinburgh Linguistics Firbush retreat, spring 2018.
- Developed and co-taught a course on data analysis for digital humanities at the University of Tartu in the spring of 2016.
- Corpus linguistics using R course for the [Academia Salensis](http://academiasalensis.org) summer school of 2015.
- Assistant for courses on language technology and artificial intelligence, Department of Computer Science, University of Tartu, 2014-2016.
<br><br>

@@

- In 2018-2019 I'm helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and neighbouring areas.
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) 2016-2018. 
- Co-organizer of the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, and head organizer of the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia. 
- Served as a student representative at various boards during my MA and MSC.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), jazz, outdoorsy stuff (cycling, hillwalking and scrambling), boardgames, and various other things. I also blog about the wonderful oddities of life abroad (but it's all in [untranslatable](http://postkaartkaledooniast.blogspot.com) Estonian).

>>>>

If you're here about materials for an upcoming workshop: [click here](https://andreskarjus.github.io/artofthefigure/).

@@

- I have been developing materials on data visualization using R; these have been used during 2017-2019 in a number of different workshops for humanities and social science audiences, collectively under the name of [_aRt of the Figure_](https://andreskarjus.github.io/artofthefigure/). All the materials are [open source](https://github.com/andreskarjus/artofthefigure).
- One outlet for these has been through the PPLS Writing Centre - the dates and booking information are available [here](http://writingcentre.ppls.ed.ac.uk/workshops/). During the semester it's a 1-hour workshop, extended to 2 hours for the extracurricular summer edition.
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page -> Book an appointment -> look for my name in the list of tutors in the 'Select staff' dropdown menu.
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).

@@

- The aRt of the Figure, interactive plots edition, at the CLE PhD retreat 2019
- The aRt of the Figure workshop as a full day session at the [Scottish Graduate School of Social Science Summer School 2018](http://www.socsciscotland.ac.uk/skills_and_training/summer_school).
- I was working with the PPLS Writing Centre in the summer of 2018 to provide a drop-in quantitative research help service for PPLS MSc students working on their theses.
- aRt of the Figure as an afternoon workshop for the annual Edinburgh Linguistics Firbush retreat, spring 2018.
- Developed and co-taught a course on data analysis for digital humanities at the University of Tartu in the spring of 2016.
- Corpus linguistics using R course for the [Academia Salensis](http://academiasalensis.org) summer school of 2015.
- Assistant for courses on language technology and artificial intelligence, Department of Computer Science, University of Tartu, 2014-2016.
<br><br>

@@

- In 2018-2019 I'm helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and neighbouring areas.
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), jazz, outdoorsy stuff (cycling, hillwalking), boardgames, and various other things. I also blog about the wonderful oddities of life abroad (but it's all in [untranslatable](http://postkaartkaledooniast.blogspot.com) Estonian).
